---
title: "Peril 7"
author: "Dave Hudson"
date: "2024-05-01"
output:
html_document:
df_print: paged
---

# R Code for Peril 7: Prior Information

#### Load libaries and wd.

```{r setup, message = FALSE}
## load libraries
library(nimble)
library(tidyverse)
library(MCMCvis)
library(coda)
library(mcmcplots)

setwd("~")
```

#### Setup sensitivity and specificity vectors and prevalence for a population of 250 individuals. Then we create test results.

```{r, message=FALSE}

psens <- c(0.75,0.7,0.9,0.65,0.6)
pspec <- c(0.55,0.7,0.65,0.75,0.6)
pprev <- 0.3
nindividuals <- 250
niter <- 100000
nburnin <- 19000
params <- c("pprev", "psens", "pspec")

#simulate infection status of the badgers
inf <- rbinom(nindividuals, 1, pprev)

#set up empty array of test outcomes
tests <- array(0, dim = c(nindividuals, length(psens)))
colnames(tests) <- c("test1", "test2", "test3", "test4", "test5")

#for each badger and each test, simulate test outcome
for(i in 1:length(inf)){
  for(j in 1:length(psens)){
    tests[i, j] <- rbinom(1, 1, ifelse(inf[i] == 1, psens[j], 1-pspec[j]))}}

#how many tests?
ntests <- 5

#get table of frequencies
binop <- 2^seq(0, ntests - 1)
testbin <- tests[, 1:ntests] %*% binop
testcounts <- tabulate(testbin + 1, nbins = 2^ntests)

#create omega matrix of binary sequence
omega <- expand.grid(replicate(ntests, c(0, 1), simplify = FALSE))
omega <- as.matrix(omega)
omega <- t(omega)

```

#### We then create a function that will create our prior beta distributions for each scenario.

```{r, message = FALSE}

# Define range
p <- seq(0, 1, length.out = 100)

### estimate beta parameters for priors
estBetaParams <- function(mu, var) {
  alpha <- ((1 - mu) / var - 1 / mu) * mu ^ 2
  beta <- alpha * (1 / mu - 1)
  return(params = list(alpha = alpha, beta = beta))
}

```

#### We now begin running the scenarios starting with vague priors.

```{r, message = FALSE, results='hide'}

code  <- nimbleCode({
  
  for(i in 1:n) {
    pinf[i] <- pprev*prod(omega[1:nT,i]*psens[1:nT]+(1-omega[1:nT,i])*(1-psens[1:nT]))+
      (1-pprev)*prod(omega[1:nT,i]*(1-pspec[1:nT])+(1-omega[1:nT,i])*(pspec[1:nT]))
  }
  Te[1:n] ~ dmulti(pinf[1:n],N)
  
  
  pprev ~ dunif(0,1)
  
  for(j in 1:nT) {
    psens[j] ~ dunif(0, 1)
    pspec[j] ~ dunif(0, 1)
  }
  
  
})

consts <- list(n = length(testcounts),
               nT = ntests, N = sum(testcounts), omega=omega)

data <- list(
  Te = testcounts)

inits <- list(
  pprev = runif(1, 0, 1),
  psens = runif(ntests, 0.5, 1),
  pspec = runif(ntests, 0.5, 1)
)

model <- nimbleModel(code, constants = consts, data = data, inits = inits)

cModel <- compileNimble(model)

config <- configureMCMC(model)

rMCMC <- buildMCMC(config)

cMCMC <- compileNimble(rMCMC, project = model)

system.time(runvagueprior <- runMCMC(cMCMC, 
                                     niter = niter, 
                                     nburnin = nburnin, 
                                     nchains = 3, 
                                     progressBar = TRUE, 
                                     summary = TRUE, 
                                     samplesAsCodaMCMC = TRUE, 
                                     thin = 1))

runvaguepriorsummary <- MCMCsummary(runvagueprior$samples)

saveRDS(runvagueprior, "VaguePrior.rds")

```

#### Now for weak/good; we will also plot the prior distributions.

```{r, message = FALSE, results='hide'}

## Set priors - Weak Good ######################################################

Se.beta <- estBetaParams(psens, 0.065)
Sp.beta <- estBetaParams(pspec, 0.065)
Pr.beta <- estBetaParams(pprev, 0.065)

plot(p, dbeta(p, Pr.beta$alpha[1], Pr.beta$beta[1]), type = 'l') #medium sens (0.75)
abline(v = 0.3, col = "red")

# Prepare the data frame for Beta distribution values
sens_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Se.beta$alpha[.x], Se.beta$beta[.x]),
  Sensitivity = paste("Sensitivity", .x),
  ActualSens = psens[.x]
))

# Plot
ggplot(sens_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Sensitivity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Sensitivity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Sensitivities",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Sensitivity"))

## Specificity
spec_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Sp.beta$alpha[.x], Sp.beta$beta[.x]),
  Specificity = paste("Specificity", .x),
  ActualSens = pspec[.x]
))

# Plot
ggplot(spec_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Specificity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Specificity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Specificity",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Specificity"))


Se.alpha <- Se.beta$alpha
Se.beta <- Se.beta$beta
Sp.alpha <- Sp.beta$alpha
Sp.beta <- Sp.beta$beta

code  <- nimbleCode({
  
  for(i in 1:n) {
    pinf[i] <- pprev*prod(omega[1:nT,i]*psens[1:nT]+(1-omega[1:nT,i])*(1-psens[1:nT]))+
      (1-pprev)*prod(omega[1:nT,i]*(1-pspec[1:nT])+(1-omega[1:nT,i])*(pspec[1:nT]))
  }
  Te[1:n] ~ dmulti(pinf[1:n],N)
  
  
  pprev ~ dbeta(Pr.beta[1], Pr.beta[2])
  
  for(j in 1:nT) {
    psens[j] ~ dbeta(Se.alpha[j], Se.beta[j])
    pspec[j] ~ dbeta(Sp.alpha[j], Sp.beta[j])
  }
  
  
})

consts <- list(n = length(testcounts), Se.beta = Se.beta, Sp.beta = Sp.beta,
               Se.alpha = Se.alpha, Sp.alpha = Sp.alpha, Pr.beta = Pr.beta,
               nT = ntests, N = sum(testcounts), omega=omega)

data <- list(
  Te = testcounts)

inits <- list(
  pprev = runif(1, 0, 1),
  psens = runif(ntests, 0.5, 1),
  pspec = runif(ntests, 0.5, 1)
)

model <- nimbleModel(code, constants = consts, data = data, inits = inits)

cModel <- compileNimble(model)

config <- configureMCMC(model)

rMCMC <- buildMCMC(config)

cMCMC <- compileNimble(rMCMC, project = model)

system.time(runWeakGood <- runMCMC(cMCMC, 
                           niter = niter, 
                           nburnin = nburnin, 
                           nchains = 3, 
                           progressBar = TRUE, 
                           summary = TRUE, 
                           samplesAsCodaMCMC = TRUE, 
                           thin = 1))


saveRDS(runWeakGood, "WeakGoodPrior.rds")

```

#### And strong/good:

```{r, message=FALSE, results='hide'}

Se.beta <- estBetaParams(psens, 0.005)
Sp.beta <- estBetaParams(pspec, 0.005)
Pr.beta <- estBetaParams(pprev, 0.005)

plot(p, dbeta(p, Pr.beta$alpha[1], Pr.beta$beta[1]), type = 'l') #medium sens (0.75)
abline(v = 0.3, col = "red")

# Prepare the data frame for Beta distribution values
sens_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Se.beta$alpha[.x], Se.beta$beta[.x]),
  Sensitivity = paste("Sensitivity", .x),
  ActualSens = psens[.x]
))

# Plot
ggplot(sens_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Sensitivity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Sensitivity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Sensitivities",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Sensitivity"))

## Specificity
spec_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Sp.beta$alpha[.x], Sp.beta$beta[.x]),
  Specificity = paste("Specificity", .x),
  ActualSens = pspec[.x]
))

# Plot
ggplot(spec_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Specificity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Specificity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Specificity",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Specificity"))


Se.alpha <- Se.beta$alpha
Se.beta <- Se.beta$beta
Sp.alpha <- Sp.beta$alpha
Sp.beta <- Sp.beta$beta

code  <- nimbleCode({
  
  for(i in 1:n) {
    pinf[i] <- pprev*prod(omega[1:nT,i]*psens[1:nT]+(1-omega[1:nT,i])*(1-psens[1:nT]))+
      (1-pprev)*prod(omega[1:nT,i]*(1-pspec[1:nT])+(1-omega[1:nT,i])*(pspec[1:nT]))
  }
  Te[1:n] ~ dmulti(pinf[1:n],N)
  
  
  pprev ~ dbeta(Pr.beta[1], Pr.beta[2])
  
  for(j in 1:nT) {
    psens[j] ~ dbeta(Se.alpha[j], Se.beta[j])
    pspec[j] ~ dbeta(Sp.alpha[j], Sp.beta[j])
  }
  
  
})

consts <- list(n = length(testcounts), Se.beta = Se.beta, Sp.beta = Sp.beta,
               Se.alpha = Se.alpha, Sp.alpha = Sp.alpha, Pr.beta = Pr.beta,
               nT = ntests, N = sum(testcounts), omega=omega)

data <- list(
  Te = testcounts)

inits <- list(
  pprev = runif(1, 0, 1),
  psens = runif(ntests, 0.5, 1),
  pspec = runif(ntests, 0.5, 1)
)

model <- nimbleModel(code, constants = consts, data = data, inits = inits)

cModel <- compileNimble(model)

config <- configureMCMC(model)

rMCMC <- buildMCMC(config)

cMCMC <- compileNimble(rMCMC, project = model)

system.time(runGoodStrong <- runMCMC(cMCMC, 
                           niter = niter, 
                           nburnin = nburnin, 
                           nchains = 3, 
                           progressBar = TRUE, 
                           summary = TRUE, 
                           samplesAsCodaMCMC = TRUE, 
                           thin = 1))

saveRDS(runGoodStrong, "GoodStrongPrior.rds")

```

#### And strong/bad:

```{r, message=FALSE, results='hide'}

## Adjust means
adjust_amount <- 0.2

# Function to adjust the vector
adjust_vec <- function(vec, adjust_amount) {
  sapply(vec, function(x) {
    # Randomly decide to add or subtract the adjustment amount
    adjustment <- ifelse(runif(1) > 0.5, adjust_amount, -adjust_amount)
    
    # Adjust the value
    new_value <- x + adjustment
    
    # Ensure the new value is within the 0 to 1 range
    if (new_value >= 1) {
      new_value <- x - adjust_amount
    } else if (new_value <= 0) {
      new_value <- x + adjust_amount
    }
    
    return(new_value)
  })
}

# Adjust the means
psensA <- adjust_vec(psens, adjust_amount)
pspecA <- adjust_vec(pspec, adjust_amount)
pprevA <- adjust_vec(pprev, adjust_amount)

Se.beta <- estBetaParams(psensA, 0.005)
Sp.beta <- estBetaParams(pspecA, 0.005)
Pr.beta <- estBetaParams(pprevA, 0.005)

plot(p, dbeta(p, Pr.beta$alpha[1], Pr.beta$beta[1]), type = 'l') #medium sens (0.75)
abline(v = 0.3, col = "red")

# Prepare the data frame for Beta distribution values
sens_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Se.beta$alpha[.x], Se.beta$beta[.x]),
  Sensitivity = paste("Sensitivity", .x),
  ActualSens = psens[.x]
))

# Plot
ggplot(sens_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Sensitivity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Sensitivity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Sensitivities",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Sensitivity"))

## Specificity
spec_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Sp.beta$alpha[.x], Sp.beta$beta[.x]),
  Specificity = paste("Specificity", .x),
  ActualSens = pspec[.x]
))

# Plot
ggplot(spec_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Specificity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Specificity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Specificity",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Specificity"))


Se.alpha <- Se.beta$alpha
Se.beta <- Se.beta$beta
Sp.alpha <- Sp.beta$alpha
Sp.beta <- Sp.beta$beta

code  <- nimbleCode({
  
  for(i in 1:n) {
    pinf[i] <- pprev*prod(omega[1:nT,i]*psens[1:nT]+(1-omega[1:nT,i])*(1-psens[1:nT]))+
      (1-pprev)*prod(omega[1:nT,i]*(1-pspec[1:nT])+(1-omega[1:nT,i])*(pspec[1:nT]))
  }
  Te[1:n] ~ dmulti(pinf[1:n],N)
  
  
  pprev ~ dbeta(Pr.beta[1], Pr.beta[2])
  
  for(j in 1:nT) {
    psens[j] ~ dbeta(Se.alpha[j], Se.beta[j])
    pspec[j] ~ dbeta(Sp.alpha[j], Sp.beta[j])
  }
  
  
})

consts <- list(n = length(testcounts), Se.beta = Se.beta, Sp.beta = Sp.beta,
               Se.alpha = Se.alpha, Sp.alpha = Sp.alpha, Pr.beta = Pr.beta,
               nT = ntests, N = sum(testcounts), omega=omega)

data <- list(
  Te = testcounts)

inits <- list(
  pprev = runif(1, 0, 1),
  psens = runif(ntests, 0.5, 1),
  pspec = runif(ntests, 0.5, 1)
)

model <- nimbleModel(code, constants = consts, data = data, inits = inits)

cModel <- compileNimble(model)

config <- configureMCMC(model)

rMCMC <- buildMCMC(config)

cMCMC <- compileNimble(rMCMC, project = model)

system.time(runBadStrong <- runMCMC(cMCMC, 
                                     niter = niter, 
                                     nburnin = nburnin, 
                                     nchains = 3, 
                                     progressBar = TRUE, 
                                     summary = TRUE, 
                                     samplesAsCodaMCMC = TRUE, 
                                     thin = 1))

saveRDS(runBadStrong, "BadStrongPrior.rds")

```

#### And finally weak/bad:

```{r, message=FALSE, results='hide'}

Se.beta <- estBetaParams(psensA, 0.045)
Sp.beta <- estBetaParams(pspecA, 0.045)
Pr.beta <- estBetaParams(pprevA, 0.045)

plot(p, dbeta(p, Pr.beta$alpha[1], Pr.beta$beta[1]), type = 'l') #medium sens (0.75)
abline(v = 0.3, col = "red")

# Prepare the data frame for Beta distribution values
sens_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Se.beta$alpha[.x], Se.beta$beta[.x]),
  Sensitivity = paste("Sensitivity", .x),
  ActualSens = psens[.x]
))

# Plot
ggplot(sens_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Sensitivity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Sensitivity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Sensitivities",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Sensitivity"))

## Specificity
spec_df <- map_df(1:5, ~ data.frame(
  p = p,
  BetaValue = dbeta(p, Sp.beta$alpha[.x], Sp.beta$beta[.x]),
  Specificity = paste("Specificity", .x),
  ActualSens = pspec[.x]
))

# Plot
ggplot(spec_df, aes(x = p, y = BetaValue)) +
  geom_line(aes(color = Specificity)) + # Line for beta distribution
  geom_vline(aes(xintercept = ActualSens, color = Specificity), linetype = "dashed") + # Matched vertical lines
  scale_color_brewer(palette = "Set1") + # Use a color palette
  labs(title = "Beta Distributions of Specificity",
       x = "Probability",
       y = "Density") +
  theme_minimal() +
  guides(color = guide_legend(title = "Specificity"))


Se.alpha <- Se.beta$alpha
Se.beta <- Se.beta$beta
Sp.alpha <- Sp.beta$alpha
Sp.beta <- Sp.beta$beta

code  <- nimbleCode({
  
  for(i in 1:n) {
    pinf[i] <- pprev*prod(omega[1:nT,i]*psens[1:nT]+(1-omega[1:nT,i])*(1-psens[1:nT]))+
      (1-pprev)*prod(omega[1:nT,i]*(1-pspec[1:nT])+(1-omega[1:nT,i])*(pspec[1:nT]))
  }
  Te[1:n] ~ dmulti(pinf[1:n],N)
  
  
  pprev ~ dbeta(Pr.beta[1], Pr.beta[2])
  
  for(j in 1:nT) {
    psens[j] ~ dbeta(Se.alpha[j], Se.beta[j])
    pspec[j] ~ dbeta(Sp.alpha[j], Sp.beta[j])
  }
  
  
})

consts <- list(n = length(testcounts), Se.beta = Se.beta, Sp.beta = Sp.beta,
               Se.alpha = Se.alpha, Sp.alpha = Sp.alpha, Pr.beta = Pr.beta,
               nT = ntests, N = sum(testcounts), omega=omega)

data <- list(
  Te = testcounts)

inits <- list(
  pprev = runif(1, 0, 1),
  psens = runif(ntests, 0.5, 1),
  pspec = runif(ntests, 0.5, 1)
)

model <- nimbleModel(code, constants = consts, data = data, inits = inits)

cModel <- compileNimble(model)

config <- configureMCMC(model)

rMCMC <- buildMCMC(config)

cMCMC <- compileNimble(rMCMC, project = model)

system.time(runBadWeak <- runMCMC(cMCMC, 
                                    niter = niter, 
                                    nburnin = nburnin, 
                                    nchains = 3, 
                                    progressBar = TRUE, 
                                    summary = TRUE, 
                                    samplesAsCodaMCMC = TRUE, 
                                    thin = 1))

saveRDS(runBadWeak, "BadWeakPrior.rds")

```

#### We then load the outputs and combine the data ready for plotting.

```{r, message=FALSE}

## Load samples
BadStrongprior <- readRDS("BadStrongPrior.rds")
GoodStrongprior <- readRDS("GoodStrongPrior.rds")
BadWeakprior <- readRDS("BadWeakPrior.rds")
WeakGoodprior <- readRDS("WeakGoodPrior.rds")
Vagueprior <- readRDS("VaguePrior.rds")

## combine data
BadStrongprior_samples <- as.matrix(BadStrongprior$samples) %>%
  as.data.frame() %>%
  select(1, 2, 7) %>%
  mutate(Prior = "Strong/Bad") %>%
  rename(Prevalence = pprev, Sensitivity = "psens[1]", Specificity = "pspec[1]", Prior = Prior) %>%
  pivot_longer(cols = c(Prevalence, Sensitivity, Specificity),  values_to = "Estimate", names_to = "Inferred_parameter" ) %>%
  mutate(Truth = rep(c(0.3, 0.75, 0.55), times = 729000/3))

GoodStrongprior_samples <- as.matrix(GoodStrongprior$samples) %>%
  as.data.frame() %>%
  select(1, 2, 7) %>%
  mutate(Prior = "Strong/Good") %>%
  rename(Prevalence = pprev, Sensitivity = "psens[1]", Specificity = "pspec[1]", Prior = Prior) %>%
  pivot_longer(cols = c(Prevalence, Sensitivity, Specificity),  values_to = "Estimate", names_to = "Inferred_parameter" ) %>%
  mutate(Truth = rep(c(0.3, 0.75, 0.55), times = 729000/3))

Vagueprior_samples <- as.matrix(Vagueprior$samples) %>%
  as.data.frame() %>%
  select(1, 2, 7) %>%
  mutate(Prior = "Vague") %>%
  rename(Prevalence = pprev, Sensitivity = "psens[1]", Specificity = "pspec[1]", Prior = Prior) %>%
  pivot_longer(cols = c(Prevalence, Sensitivity, Specificity),  values_to = "Estimate", names_to = "Inferred_parameter" ) %>%
  mutate(Truth = rep(c(0.3, 0.75, 0.55), times = 729000/3))

BadWeakprior_samples <- as.matrix(BadWeakprior$samples) %>%
  as.data.frame() %>%
  select(1, 2, 7) %>%
  mutate(Prior = "Weak/Bad") %>%
  rename(Prevalence = pprev, Sensitivity = "psens[1]", Specificity = "pspec[1]", Prior = Prior) %>%
  pivot_longer(cols = c(Prevalence, Sensitivity, Specificity),  values_to = "Estimate", names_to = "Inferred_parameter" ) %>%
  mutate(Truth = rep(c(0.3, 0.75, 0.55), times = 729000/3))

WeakGoodprior_samples <- as.matrix(WeakGoodprior$samples) %>%
  as.data.frame() %>%
  select(1, 2, 7) %>%
  mutate(Prior = "Weak/Good") %>%
  rename(Prevalence = pprev, Sensitivity = "psens[1]", Specificity = "pspec[1]", Prior = Prior) %>%
  pivot_longer(cols = c(Prevalence, Sensitivity, Specificity),  values_to = "Estimate", names_to = "Inferred_parameter" ) %>%
  mutate(Truth = rep(c(0.3, 0.75, 0.55), times = 729000/3))

plot_data <- rbind(BadStrongprior_samples, GoodStrongprior_samples, BadWeakprior_samples, WeakGoodprior_samples, Vagueprior_samples)

```

#### And finally we can plot.

```{r, message=FALSE}

plot5test <- ggplot(plot_data, aes(x = Inferred_parameter, y = Estimate, fill = Inferred_parameter)) +
  geom_violin() +
  stat_summary(fun = "mean", geom = "point") +
  labs(x = "Prior Information", y = "Inferred parameter", fill = "Inferred parameter", colour = "Inferred parameter") +
  #facet_grid( ~ Prior) + 
  facet_grid(~ factor(Prior, levels=c('Strong/Bad', 'Strong/Good', 'Weak/Bad', 'Weak/Good', 'Vague'))) +
  geom_hline(aes(yintercept = Truth, colour = Inferred_parameter), linetype = 2) +
  theme_bw() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), text = element_text(size = 15))

plot5test + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

```

