---
title: "Peril 1"
author: "Dave Hudson"
date: "2024-05-01"
output:
html_document:
df_print: paged
---

# R Code for Peril 1: Insufficient Tests

#### Load libaries and set wd

```{r setup, message = FALSE}
library(nimble)
library(MCMCvis)
library(tidyverse)
library(coda)

setwd("~")
```

#### Setup test parameters

#### Set sensitivities and specificities for five different tests and prevalences for a single population of 1000 individuals and store true values

```{r, message = FALSE}
psens <- c(0.85, 0.8, 0.7, 0.6, 0.5)
pspec <- c(0.70, 0.85, 0.75, 0.65, 0.55)
pprev <- 0.3
nindiv <- 1000
true_values <- c(pprev, psens[1], pspec[1])
true_parameter <- c("Prevalence", "Sensitivity", "Specificity")
truth <- data.frame(true_parameter, true_values)
```

#### Simulate infection status of the individuals

```{r, message = FALSE}
inf <- rbinom(nindiv, 1, pprev)
```

#### Set up empty array of test outcomes and simulate test outcomes

```{r, message = FALSE}
tests <- array(0, dim = c(nindiv, length(psens)))
colnames(tests) <- c("test1", "test2", "test3", "test4", "test5")

for(i in 1:length(inf)){
  for(j in 1:length(psens)){
    tests[i, j] <- rbinom(1, 1, ifelse(inf[i] == 1, psens[j], 1-pspec[j]))}}
```

#### Now we run the analysis using the results from one test, we first create a table of results before fitting a model in NIMBLE and saving the output.

```{r, message = FALSE}
ntests <- 1

#get table of frequencies
binop <- 2^seq(0, ntests-1)
testbin <- tests[, 1:ntests] #%*% binop
testcounts <- tabulate(testbin + 1, nbins = 2^ntests)
testcounts

#create omega matrix of binary sequence
omega <- expand.grid(replicate(ntests, c(0, 1), simplify = FALSE))
omega <- as.matrix(omega)
omega <- t(omega)

## Define parameters you want to report on
params <- c("pprev", "psens", "pspec")

code  <- nimbleCode({
  
  for(i in 1:n) {
    pinf[i] <- pprev * (omega[1, i] * psens + (1 - omega[1, i]) * (1 - psens)) +
      (1 - pprev) * (omega[1, i] * (1 - pspec) + (1 - omega[1, i]) * (pspec))
  }
  
  Te[1:n] ~ dmulti(pinf[1:n], N)
  
  
  pprev ~ dunif(0, 1)
  psens ~ dunif(0.5, 1)
  pspec ~ dunif(0.5, 1)
  
})

consts <- list(n = length(testcounts),
               N = sum(testcounts), omega = omega)

data <- list(
  Te = testcounts)

inits <- list(
  pprev = runif(1, 0, 1),
  psens = runif(1, 0.5, 1),
  pspec = runif(1, 0.5, 1)
)

model <- nimbleModel(code, constants = consts, data = data, inits = inits)

cModel <- compileNimble(model)

config <- configureMCMC(model)

rMCMC <- buildMCMC(config)

cMCMC <- compileNimble(rMCMC, project = model)

system.time(run <- runMCMC(cMCMC, 
                           niter = 80000, 
                           nburnin = 12000, 
                           nchains = 3, 
                           progressBar = TRUE, 
                           summary = TRUE, 
                           samplesAsCodaMCMC = TRUE, 
                           thin = 1))

saveRDS(run, file = "run1.rds")

```

#### Having completed the analysis for 1 test we now repeat the next block of code for 2-5 tests, each time we save the output ready for plotting.

```{r, message = FALSE, results='hide'}

for (ntests in 2:5) {
  # Get table of frequencies
  binop <- 2^seq(0, ntests-1)
  testbin <- tests[, 1:ntests] %*% binop
  testcounts <- tabulate(testbin + 1, nbins = 2^ntests)

  # Create omega matrix of binary sequence
  omega <- expand.grid(replicate(ntests, c(0, 1), simplify = FALSE))
  omega <- as.matrix(omega)
  omega <- t(omega)

  # Define parameters you want to report on
  params <- c("pprev", "psens", "pspec")

  # Nimble code for the model
  code <- nimbleCode({
    for(i in 1:n) {
      pinf[i] <- pprev * prod(omega[1:nT, i] * psens[1:nT] + (1 - omega[1:nT, i]) * (1 - psens[1:nT])) +
        (1 - pprev) * prod(omega[1:nT, i] * (1 - pspec[1:nT]) + (1 - omega[1:nT, i]) * (pspec[1:nT]))
    }
    Te[1:n] ~ dmulti(pinf[1:n], N)
    pprev ~ dunif(0, 1)
    for(j in 1:nT) {
      psens[j] ~ dunif(0.5, 1)
      pspec[j] ~ dunif(0.5, 1)
    }
  })

  # Constants and data for the model
  consts <- list(n = length(testcounts), nT = ntests, N = sum(testcounts), omega = omega)
  data <- list(Te = testcounts)
  inits <- list(pprev = runif(1, 0, 1), psens = runif(ntests, 0.5, 1), pspec = runif(ntests, 0.5, 1))

  # Building and compiling the model
  model <- nimbleModel(code, constants = consts, data = data, inits = inits)
  cModel <- compileNimble(model)
  config <- configureMCMC(model)
  rMCMC <- buildMCMC(config)
  cMCMC <- compileNimble(rMCMC, project = model)

  # Running MCMC
  system.time(run <- runMCMC(cMCMC, 
                             niter = 80000, 
                             nburnin = 12000, 
                             nchains = 3, 
                             progressBar = TRUE, 
                             summary = TRUE, 
                             samplesAsCodaMCMC = TRUE, 
                             thin = 1))

  # Save the run with a dynamic filename
  saveRDS(run, file = paste0("run", ntests, ".rds"))
}
```

#### Now load the results from all runs into the local environment

```{r, message = FALSE}

run1 <- readRDS("run1.rds")
run2 <- readRDS("run2.rds")
run3 <- readRDS("run3.rds")
run4 <- readRDS("run4.rds")
run5 <- readRDS("run5.rds")
```


#### We now process the results getting ready to plot

```{r, message = FALSE}

## Do run1 first
r1_sum <- run1$summary
r1_sum <- as.matrix(r1_sum$all.chains[, 1])
r1_samp <- as.matrix(run1$samples)

r1_samp <- r1_samp %>%
  as.data.frame() %>%
  pivot_longer(cols = c(pprev, psens, pspec),  values_to = "Estimate", names_to = "Inferred_parameter" ) %>%
  mutate(NumberOfTests = 1) %>%
  mutate(Truth = rep(c(0.3, 0.85, 0.7), times = 612000/3)) %>%
  mutate(Mean = rep(c(r1_sum[1], r1_sum[2], r1_sum[3]), times = 612000/3))

## Now for runs 2-5
runs <- list(run2, run3, run4, run5)

# Initialize an empty list to store the processed data frames
data_frames <- list()

# Loop over each run
for (i in 1:length(runs)) {
  # Get summary and samples
  run_sum <- runs[[i]]$summary
  run_sum <- as.matrix(run_sum$all.chains[, 1])
  run_samp <- as.matrix(runs[[i]]$samples)
  
  # Convert to data frame and reshape
  run_samp <- run_samp %>%
    as.data.frame() %>%
    rename(pprev = 1, psens = 2, psens2 = 3, pspec = 4, pspec2 = 5) %>%
    pivot_longer(cols = c(pprev, psens, pspec), names_to = "Inferred_parameter", values_to = "Estimate") %>%
    mutate(NumberOfTests = i + 1,
           Truth = rep(c(0.3, 0.85, 0.7), times = 612000 / 3),
           Mean = rep(run_sum[1:3], times = 612000 / 3))
  
  # Store in list
  data_frames[[i]] <- run_samp
}

# Combine all data frames into one
data <- bind_rows(r1_samp, data_frames) %>%
  select(1:5)
```

#### We can now do a bit of tidying and create the plot

```{r, message = FALSE}

data$NumberOfTests <- as.factor(data$NumberOfTests)
data <- data %>%
  mutate(Inferred_parameter = c(rep(c("Prevalence", "Sensitivity", "Specificity"), times = 3060000/3)))
                                

ggplot(data, aes(x = Inferred_parameter, y = Estimate, fill = Inferred_parameter)) +
  geom_violin(position = "dodge") +
  geom_hline(aes(yintercept = Truth, colour = Inferred_parameter), linetype = 2) +
  stat_summary(fun = "mean", geom = "point") +
  facet_grid(~ NumberOfTests) +
  theme_bw() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), text = element_text(size = 15)) +
  labs(x = "Number of Tests", fill = "Inferred parameter", colour = "Inferred parameter")

```







