---
title: "Peril 2"
author: "Dave Hudson"
date: "2024-05-01"
output:
html_document:
df_print: paged
---

# R Code for Peril 2: Alternatives to a 3rd test

#### Load libaries and set wd.

```{r setup, message = FALSE}
library(nimble)
library(MCMCvis)
library(tidyverse)
library(coda)

setwd("~")
```

#### Setup test parameters

#### Set sensitivities and specificities for two different tests and prevalences for two populations of 1000 individuals where the prevalence of the second population changes.

```{r, message = FALSE}
psens <- c(0.9, 0.9)
pspec <- c(0.75, 0.75)
npopns<-2

# Define the range of second prevalence values
prevalence_values <- seq(0.3, 0.5, by = 0.05)
```

#### Now we loop over the analysis for each of the different prevalence values for the second population and save the output.

```{r, message = FALSE, results='hide'}
# Loop through each prevalence value
for (pprev2 in prevalence_values) {
  pprev <- c(0.3, pprev2)  # First prevalence fixed at 0.3, second varies
  nbadgers <- 1000
  npopns <- length(pprev)  # Update number of populations based on prevalence vector length

  # Simulate infection status of the badgers
  inf <- array(0, dim = c(nbadgers, npopns))
  for(p in 1:npopns){
    inf[, p] <- rbinom(nbadgers, 1, pprev[p])
  }
  
  # Set up empty array of test outcomes
  tests <- array(0, dim = c(nbadgers, length(psens), npopns))
  colnames(tests) <- c("test1", "test2")
  
  # Simulate test outcomes
  for(p in 1:npopns){
    for(i in 1:nbadgers){
      for(j in 1:length(psens)){
        tests[i, j, p] <- rbinom(1, 1, ifelse(inf[i, p] == 1, psens[j], 1 - pspec[j]))
      }
    }
    
    # Get table of frequencies
    ntests <- 2
    binop <- 2^seq(0, ntests-1)
    testbin <- array(0, dim = c(nbadgers, npopns))
    testcounts <- array(0, dim = c(2^ntests, npopns))
    for(p in 1:npopns){
      testbin[,p] <- tests[, 1:ntests, p] %*% binop
      testcounts[,p] <- tabulate(testbin[,p] + 1, nbins = 2^ntests)
    }
    
    # Create omega matrix of binary sequence
    omega <- t(as.matrix(expand.grid(replicate(ntests, c(0, 1), simplify = FALSE))))
    
    ## Define parameters you want to report on
    params <- c("pprev", "psens", "pspec")
    
    code  <- nimbleCode({
      
      for(p in 1:nP){
        for(i in 1:n) {
          pinf[i, p] <- pprev[p] * prod(omega[1:nT, i] * psens[1:nT] + (1 - omega[1:nT, i]) * (1 - psens[1:nT]))+
            (1 - pprev[p]) * prod(omega[1:nT, i] * (1 - pspec[1:nT]) + (1 - omega[1:nT, i]) * (pspec[1:nT]))
        }
        Te[1:n, p] ~ dmulti(pinf[1:n, p], N)
      }
      
      for(p in 1:npopns){ 
        pprev[p] ~ dunif(0,1)
      }
      
      for(j in 1:nT) {
        psens[j] ~ dunif(0, 1)
        pspec[j] ~ dunif(0, 1)
      }
      
      
    })
    
    consts <- list(n = 2^ntests,
                   nT = ntests, N = nbadgers, omega=omega, nP = npopns)
    
    data <- list(
      Te = testcounts)
    
    inits <- list(
      pprev = runif(npopns, 0, 1),
      psens = runif(ntests, 0.5, 1),
      pspec = runif(ntests, 0.5, 1)
    )
    
    model <- nimbleModel(code, constants = consts, data = data, inits = inits)
    
    cModel <- compileNimble(model)
    
    config <- configureMCMC(model)
    
    rMCMC <- buildMCMC(config)
    
    cMCMC <- compileNimble(rMCMC, project = model)
    
    system.time(run <- runMCMC(cMCMC, 
                               niter = 50000, 
                               nburnin = 2400, 
                               nchains = 3, 
                               progressBar = TRUE, 
                               summary = TRUE, 
                               samplesAsCodaMCMC = TRUE, 
                               thin = 1))
    
    # Save the run
    save_filename <- sprintf("run_%03d.rds", round(pprev2 * 100))
    saveRDS(run, save_filename)
  }
}

```

#### Now load the results from all runs into the local environment

```{r, message = FALSE}

r50 <- readRDS("run_050.rds")
r45 <- readRDS("run_045.rds")
r40 <- readRDS("run_040.rds")
r35 <- readRDS("run_035.rds")
r30 <- readRDS("run_030.rds")
```


#### We now process the results getting ready to plot

```{r, message = FALSE}

# List of run objects and their respective second prevalence values
runs <- list(r50 = 0.5, r45 = 0.45, r40 = 0.4, r35 = 0.35, r30 = 0.3)
data_frames <- list()

# Loop over each run and its associated prevalence value
for (run in names(runs)) {
  current_run <- get(run)  # using 'get' to retrieve the run object based on its name
  
  # Summarize and transform data
  run_sum <- as.matrix(current_run$summary$all.chains[, 1])
  run_samp <- as.matrix(current_run$samples)
  
  run_samp <- run_samp %>%
    as.data.frame() %>%
    rename(PrevalenceA = 1, PrevalenceB = 2, Sensitivity = 3, Sensitivity2 = 4, Specificity = 5, Specificity2 = 6) %>%
    select(PrevalenceA, PrevalenceB, Sensitivity, Specificity) %>%
    pivot_longer(cols = c(PrevalenceA, PrevalenceB, Sensitivity, Specificity), 
                 values_to = "Estimate", names_to = "Inferred_parameter") %>%
    mutate(Truth = rep(c(0.3, runs[[run]], 0.9, 0.75), times = 571200/4)) %>%
    mutate(Mean = rep(run_sum[1:4], times = 571200/4)) %>%
    mutate(PrevalenceB_truth = runs[[run]])
  
  # Store in list
  data_frames[[run]] <- run_samp
}

# Combine all data frames into one final data frame
data <- bind_rows(data_frames)

```

#### We can now do a bit of tidying and create the plot

```{r, message = FALSE}

ggplot(data, aes(x = Inferred_parameter, y = Estimate, fill = Inferred_parameter)) +
  geom_violin(position = "dodge") +
  geom_hline(aes(yintercept = Truth, colour = Inferred_parameter), linetype = 2) +
  stat_summary(fun = "mean", geom = "point") +
  facet_grid(~ PrevalenceB_truth) +
  theme_bw() +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), text = element_text(size = 15)) +
  labs(x = "Prevalence Population B", fill = "Inferred parameter", colour = "Inferred parameter")

```







