---
title: "Peril 6"
author: "Dave Hudson"
date: "2024-05-01"
output:
html_document:
df_print: paged
---

# R Code for Peril 6: Trade-offs between Sensitivity and Specificity

#### Load libaries and wd.

```{r setup, message = FALSE}
library(nimble)
library(MCMCvis)
library(tidyverse)
library(coda)
library(patchwork)
library(GGally)

setwd("~")
```

#### Setup sensitivity and specificity vector, number of tests and number of simulations we want to run. we then setup a number of 3D arrays to store the results of the simulations.

```{r, message=FALSE}

## set up initial parameters, number of tests and iterations
ntests <- 5
psensvec <- c(0.55, 0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95)
pspecvec <- c(0.95, 0.9, 0.85, 0.8, 0.75, 0.7, 0.65, 0.6, 0.55)
n_iterations <- 20

## initialize a 3D array to store the summary statistics
summaryinference_all <- array(0, dim = c(n_iterations, length(psensvec), 2 * ntests + 1))
summaryinfsd_all <- array(0, dim = c(n_iterations, length(psensvec), 2 * ntests + 1))

```

#### We now run a series of loops, first over the number of simulations we want and then for each simulation we loop over the sensitivity vector. Please note that we use an informative prior on the prevalence to try and limit the number of simulations that return the flipped parameter solution (although this will likely not eliminate them) but leave uninformative priors on both sensitivity and specificity.

```{r, message = FALSE, results='hide'}

## Begin loop over iterations
for(iter in 1:n_iterations) {
  
  # Initialize summaryinference and summaryinfsd inside the loop over iterations
  summaryinference <- matrix(0, nrow = length(psensvec), ncol = 2 * ntests + 1)
  summaryinfsd <- matrix(0, nrow = length(psensvec), ncol = 2 * ntests + 1)
  
  ## Begin loop over sensitivities
  for(q in 1:length(psensvec)){
    
    psens <- c(psensvec[q], 0.8, 0.7, 0.65, 0.6)
    pspec <- c(pspecvec[q], 0.75, 0.7, 0.65, 0.6)
    pprev <- 0.3
    nindividuals <- 1000
    print(psens)
    print(pspec)
    print(pprev)
    
    #simulate infection status of the badgers
    inf <- rbinom(nindividuals, 1, pprev)
    
    #set up empty array of test outcomes
    tests <- array(0, dim = c(nindividuals, length(psens)))
    colnames(tests) <- c("test1", "test2", "test3", "test4", "test5")
    
    #for each badger and each test, simulate test outcome
    for(i in 1:length(inf)){
      for(j in 1:length(psens)){
        tests[i, j] <- rbinom(1, 1, ifelse(inf[i] == 1, psens[j], 1 - pspec[j]))}}
    
    ############manipulate test numbers from here###############
    
    #get table of frequencies
    binop <- 2^seq(0, ntests - 1)
    testbin <- tests[, 1:ntests] %*% binop
    testcounts <- tabulate(testbin + 1, nbins = 2^ntests)
    testcounts
    
    #create omega matrix of binary sequence
    omega <- expand.grid(replicate(ntests, c(0, 1), simplify = FALSE))
    omega <- as.matrix(omega)
    omega <- t(omega)
    
    code  <- nimbleCode({
      
      for(i in 1:n) {
        
        pinf[i] <- pprev * prod(omega[1:nT, i] * psens[1:nT] + (1 - omega[1:nT, i]) * (1 - psens[1:nT])) +
          (1 - pprev) * prod(omega[1:nT, i] * (1-pspec[1:nT]) + (1 - omega[1:nT, i]) * (pspec[1:nT]))
      }
      
      for(k in 1:nT){
        psens[k] ~ dunif(0, 1)
        pspec[k] ~ dunif(0, 1)
      }
      
      pprev ~ dunif(0, 0.5)
      
      Te[1:n] ~ dmulti(pinf[1:n], N)
      
    })
    
    consts <- list(n = length(testcounts),
                   nT = ntests, N = sum(testcounts), omega = omega)
    
    data <- list(
      Te = testcounts)
    
    inits <- list(
      pprev = runif(1, 0, 0.5),
      psens = runif(ntests, 0.5, 1),
      pspec = runif(ntests, 0.5, 1)
    )
    
    model <- nimbleModel(code, constants = consts, data = data, inits = inits)
    
    cModel <- compileNimble(model)
    
    config <- configureMCMC(model)
    
    
    rMCMC <- buildMCMC(config)
    
    cMCMC <- compileNimble(rMCMC, project = model)
    
    system.time(run <- runMCMC(cMCMC, 
                               niter = 10000, 
                               nburnin = 2400, 
                               nchains = 3, 
                               progressBar = TRUE, 
                               summary = TRUE, 
                               samplesAsCodaMCMC = TRUE, 
                               thin = 1))
    
    runsummary <- MCMCsummary(run$samples)
    
    summaryinference[q, ] <- runsummary$mean
    summaryinfsd[q, ] <- runsummary$sd
    
  } # end loop over sensitivities
  
  summaryinference_all[iter, , ] <- summaryinference
  summaryinfsd_all[iter, , ] <- summaryinfsd  
  
} # end loop over iterations

## Save data
saveRDS(summaryinference_all, "SummaryInference_ALL2.rds")
saveRDS(summaryinfsd_all, "SummaryInfSD_ALL2.rds")

## Save last run for Figure 9
saveRDS(run, "FinalRunSamples2.rds")

```

#### We now load the results and process ready to plot.

```{r, message = FALSE, results='hide'}

summaryinference_all <- readRDS("SummaryInference_ALL2.rds")
summaryinfsd_all <- readRDS("SummaryInfSD_ALL2.rds")

# Create an empty data frame to hold the results
plot_data <- data.frame(iteration = integer(),
                        true_sens = double(),
                        true_spec = double(),
                        true_prev = double(),
                        inferred_sens = double(),
                        inferred_spec = double(),
                        inferred_prev = double())

# Loop through the 3D arrays to populate the data frame
for (iter in 1:dim(summaryinference_all)[1]) {
  for (q in 1:dim(summaryinference_all)[2]) {
    true_sens = psensvec[q]
    true_spec = pspecvec[q]
    true_prev = 0.3
    
    # Replace x, y with the indices where inferred_sens and posterior_sd are stored
    inferred_sens = summaryinference_all[iter, q, 2]
    inferred_spec = summaryinference_all[iter, q, 7]
    inferred_prev = summaryinference_all[iter, q, 1]

    plot_data <- rbind(plot_data, data.frame(iteration = iter, true_sens = true_sens,  true_spec = true_spec,
                                             true_prev = true_prev,
                                             inferred_sens = inferred_sens, inferred_prev = inferred_prev,
                                             inferred_spec = inferred_spec))
  }
}

# Create an empty data frame to hold the results
plot_dataSD <- data.frame(iteration = integer(),
                        true_sens = double(),
                        true_spec = double(),
                        inferred_sensSD = double(),
                        inferred_specSD = double(),
                        inferred_prevSD = double())

# Loop through the 3D arrays to populate the data frame
for (iter in 1:dim(summaryinfsd_all)[1]) {
  for (q in 1:dim(summaryinfsd_all)[2]) {
    true_sens = psensvec[q]
    true_spec = pspecvec[q]
    
    # inferred_sens and posterior_sd are stored
    inferred_sensSD = summaryinfsd_all[iter, q, 2]
    inferred_specSD = summaryinfsd_all[iter, q, 7]
    inferred_prevSD = summaryinfsd_all[iter, q, 1]
    
    plot_dataSD <- rbind(plot_dataSD, data.frame(iteration = iter, true_sens = true_sens,  true_spec = true_spec,
                                             inferred_sensSD = inferred_sensSD, inferred_prevSD = inferred_prevSD,
                                             inferred_specSD = inferred_specSD))
  }
}

```

#### Now prepare each panel plot.

```{r, message = FALSE}

# Asd - Within sample imprecision
aSD <- plot_dataSD %>%
  group_by(true_sens) %>%
  mutate(Asd = inferred_sensSD) %>%
  ungroup() %>%
  ggplot(aes(x = true_sens, y = Asd)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Within sample imprecision") +
  theme_bw() +
  theme(text = element_text(size = 13),
        axis.title.y = element_text(size = 10))

# Bsd - Within sample imprecision
bSD <- plot_dataSD %>%
  group_by(true_sens) %>%
  mutate(Asd = inferred_specSD) %>%
  ungroup() %>%
  ggplot(aes(x = true_sens, y = Asd)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Within sample imprecision") +
  theme_bw() +
  theme(text = element_text(size = 13),
        axis.title.y = element_text(size = 10))
  
# Csd - Within sample imprecision
cSD <- plot_dataSD %>%
  group_by(true_sens) %>%
  mutate(Asd = inferred_prevSD) %>%
  ungroup() %>%
  ggplot(aes(x = true_sens, y = Asd)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Within sample imprecision") +
  theme_bw() +
  theme(text = element_text(size = 13),
        axis.title.y = element_text(size = 10))

# A - Sensitivity
a <- ggplot(plot_data, aes(x = true_sens, y = inferred_sens)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Sensitivity") +
  geom_abline(slope = 1,
              intercept = 0,
              color="blue") +
  theme_bw() +
  theme(text = element_text(size = 13))

# B - Specificity
b <- ggplot(plot_data, aes(x = true_sens, y = inferred_spec)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Specificity") +
  geom_abline(slope = -1,
              intercept = 1.5,
              color="blue")  +
  theme_bw() +
  theme(text = element_text(size = 13))

# C - Prevalence
c <- ggplot(plot_data, aes(x = true_sens, y = inferred_prev)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Prevalence") +
  geom_hline(yintercept = 0.3,
              color="blue") +
  theme_bw() +
  theme(text = element_text(size = 13))
  
## Prepare data
plot_data1 <- plot_data %>%
  group_by(true_sens) %>%
  mutate(DiffSens = inferred_sens - true_sens) %>%
  mutate(DiffSpec = inferred_spec - true_spec) %>%
  mutate(DiffPrev = inferred_prev - 0.3)

# A1 - Within sample inaccuracy
a1 <- ggplot(plot_data1, aes(x = true_sens, y = DiffSens)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Within sample inaccuracy") +
  geom_abline(slope = 0,
              intercept = 0,
              color="black") +
  theme_bw() +
  theme(text = element_text(size = 13),
        axis.title.y = element_text(size = 10))

# B1 - Within sample inaccuracy
b1 <- ggplot(plot_data1, aes(x = true_sens, y = DiffSpec)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Within sample inaccuracy") +
  geom_abline(slope = 0,
              intercept = 0,
              color="black") +
  theme_bw() +
  theme(text = element_text(size = 13),
        axis.title.y = element_text(size = 10))
  
# C1 - Within sample inaccuracy
c1 <- ggplot(plot_data1, aes(x = true_sens, y = DiffPrev)) +
  geom_point(alpha = 0.2) +
  xlab("") +
  ylab("Within sample inaccuracy") +
  geom_abline(slope = 0,
              intercept = 0,
              color="black") +
  theme_bw() +
  theme(text = element_text(size = 13),
        axis.title.y = element_text(size = 10))

```

#### And finally generate the final plot.

```{r, message=FALSE}

Fig7 <- (a/b/c)|(a1/b1/c1)|(aSD/bSD/cSD)

wrap_elements(panel = Fig7) +
  labs(tag = "True Sensitivity") +
  theme(
    plot.tag = element_text(size = 13),
    plot.tag.position = "bottom"
  )

```

#### We now move to Figure 8: Associations among diagnostic parameters inferred from replicated simulations of diagnostic testing regimes.

#### First set test sensitivities and specificities for three different tests and prevalence for a single population of 1000 individuals.

```{r, message=FALSE}

psens <- c(0.85, 0.8, 0.7)
pspec <- c(0.70, 0.85, 0.75)
pprev <- 0.3
nindividuals <- 1000
true_values <- c(pprev, psens[1], pspec[1])
true_parameter <- c("Prevalence", "Sensitivity", "Specificity")
truth <- data.frame(true_parameter, true_values)
```

#### Now set the number of simulations we want to run and the number of tests.

```{r}
n_iterations <- 30
ntests <- 3
```

#### We then set an array to store the results before strating the run. Please note that again we use an informative prior on prevalence but not on sensitivty and specificity.

```{r, message=FALSE, results='hide'}

# Initialize summary inference
summaryinfMean <- matrix(0, nrow = n_iterations, ncol = 2 * ntests + 1)

## Begin loop over iterations
for(iter in 1:n_iterations) {
  
  #simulate infection status of the badgers
  inf <- rbinom(nindividuals, 1, pprev)

  #set up empty array of test outcomes
  tests <- array(0, dim = c(nindividuals, length(psens)))
  colnames(tests) <- c("test1", "test2", "test3")
  
  #for each badger and each test, simulate test outcome
  for(i in 1:length(inf)){
    for(j in 1:length(psens)){
      tests[i, j] <- rbinom(1, 1, ifelse(inf[i] == 1, psens[j], 1-pspec[j]))}}
  
  #get table of frequencies
  binop <- 2^seq(0, ntests-1)
  testbin <- tests[, 1:ntests] %*% binop
  testcounts <- tabulate(testbin + 1, nbins = 2^ntests)
  testcounts
  
  #create omega matrix of binary sequence
  omega <- expand.grid(replicate(ntests, c(0, 1), simplify = FALSE))
  omega <- as.matrix(omega)
  omega <- t(omega)
  
  ## Define parameters you want to report on
  params <- c("pprev", "psens", "pspec")
  
  code  <- nimbleCode({
    
    for(i in 1:n) {
      pinf[i] <- pprev * prod(omega[1:nT, i] * psens[1:nT] + (1 - omega[1:nT, i]) * (1 - psens[1:nT])) +
        (1 - pprev) * prod(omega[1:nT, i] * (1 - pspec[1:nT]) + (1 - omega[1:nT, i]) * (pspec[1:nT]))
    }
    
    Te[1:n] ~ dmulti(pinf[1:n], N)
    
    
    pprev ~ dunif(0, 0.5)
    
    for(j in 1:nT) {
      psens[j] ~ dunif(0, 1)
      pspec[j] ~ dunif(0, 1)
    }
    
  })
  
  consts <- list(n = length(testcounts),
                 nT = ntests, N = sum(testcounts), omega = omega)
  
  data <- list(
    Te = testcounts)
  
  inits <- list(
    pprev = runif(1, 0, 0.5),
    psens = runif(ntests, 0.5, 1),
    pspec = runif(ntests, 0.5, 1)
  )
  
  model <- nimbleModel(code, constants = consts, data = data, inits = inits)
  
  cModel <- compileNimble(model)
  
  config <- configureMCMC(model)
  
  rMCMC <- buildMCMC(config)
  
  cMCMC <- compileNimble(rMCMC, project = model)
  
  system.time(run <- runMCMC(cMCMC, 
                             niter = 80000, 
                             nburnin = 12000, 
                             nchains = 3, 
                             progressBar = TRUE, 
                             summary = TRUE, 
                             samplesAsCodaMCMC = TRUE, 
                             thin = 1))
  
  runsummary <- MCMCsummary(run$samples)
  
  summaryinfMean[iter, ] <- runsummary$mean
  
  } # end loop over sensitivities

saveRDS(summaryinfMean, "SummaryInfMean2.rds")

```

#### We now load the results, adjust column names and plot.

```{r, message = FALSE}

summaryinfMean <- as.data.frame(readRDS("SummaryInfMean2.rds"))
colnames(summaryinfMean) <- c("Prev", "Se1", "Se2", "Se3", "Sp1", "Sp2", "Sp3")

# fig 8
ggpairs(summaryinfMean, aes(alpha = 0.2)) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(text = element_text(size = 15), axis.text.x = element_text(size = 8), axis.text.y = element_text(size = 8))

```

#### Now for Figure 9 - first we load the output we saved earlier and do some tidying.

```{r, message=FALSE}

## Pairs plot
run <- readRDS("FinalRunSamples.rds")

rundf <- as.matrix(run$samples, chain = TRUE) %>%
  as.data.frame() %>%
  mutate(CHAIN = as.factor(CHAIN))
```

#### We then thin the samples out to reduce overplotting.

```{r, message=FALSE}
# thin samples
rundf_filtered <- rundf[seq(1, nrow(rundf), 200), ]
colnames(rundf_filtered) <- c("CHAIN", "Prev", "Se1", "Se2", "Se3", "Sp1", "Sp2", "Sp3")
```

#### And then plot.

```{r, message=FALSE}

# fig 9
ggpairs(rundf_filtered, columns = 2:8, aes(colour = CHAIN, alpha = 0.1)) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  theme(text = element_text(size = 15), axis.text.x = element_text(size = 8), axis.text.y = element_text(size = 8)) +
  theme(axis.ticks = element_blank())
```
