---
title: "Peril 5"
author: "Dave Hudson"
date: "2024-05-01"
output:
html_document:
df_print: paged
---

# R Code for Peril 5: Precision and Accuracy at the Boundaries of Truth

#### Load libaries and wd.

```{r setup, message = FALSE}
library(nimble)
library(MCMCvis)
library(tidyverse)
library(coda)
library(patchwork)

setwd("~")
```

#### Setup sensitivity vector, number of tests and number of simulations we want to run. we then setup a number of 3D arrays to store the results of the simulations.

```{r, message=FALSE}

ntests <- 5
psensvec <- c(0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 0.98, 0.99)
n_iterations <- 20

## initialize a 3D array to store the summary statistics
summaryinference_all <- array(0, dim = c(n_iterations, length(psensvec), 2 * ntests + 1))
summaryinfsd_all <- array(0, dim = c(n_iterations, length(psensvec), 2 * ntests + 1))

```

#### We now run a series of loops, first over the number of simulations we want and then for each simulation we loop over the sensitivity vector. Please note that we do not use informative priors so run the risk of having some simulations that return the flipped parameter solution.

```{r, echo = FALSE, message = FALSE, results='hide'}

## Begin loop over iterations
for(iter in 1:n_iterations) {
  
  # Initialize summary inference inside the loop over iterations
  summaryinference <- matrix(0, nrow = length(psensvec), ncol = 2 * ntests + 1)
  summaryinfsd <- matrix(0, nrow = length(psensvec), ncol = 2 * ntests + 1)
 
  ## Begin loop over sensitivities
  for(q in 1:length(psensvec)){
    
    psens <- c(psensvec[q], 0.8, 0.7, 0.65, 0.6)
    pspec <- c(0.75, 0.7, 0.65, 0.6, 0.55)
    pprev <- 0.3
    nindividuals <- 1000
    
    #simulate infection status
    inf <- rbinom(nindividuals, 1, pprev)
    
    #set up empty array of test outcomes
    tests <- array(0, dim = c(nindividuals, length(psens)))
    colnames(tests) <- c("test1", "test2", "test3", "test4", "test5")
    
    #for each individual and each test, simulate test outcome
    for(i in 1:length(inf)){
      for(j in 1:length(psens)){
        tests[i, j] <- rbinom(1, 1, ifelse(inf[i] == 1, psens[j], 1 - pspec[j]))}}
    
    ############manipulate test numbers from here###############
    
    #get table of frequencies
    binop <- 2^seq(0, ntests - 1)
    testbin <- tests[, 1:ntests] %*% binop
    testcounts <- tabulate(testbin + 1, nbins = 2^ntests)
    testcounts
    
    #create omega matrix of binary sequence
    omega <- expand.grid(replicate(ntests, c(0, 1), simplify = FALSE))
    omega <- as.matrix(omega)
    omega <- t(omega)
    
    code  <- nimbleCode({
      
      for(i in 1:n) {
        
        pinf[i] <- pprev * prod(omega[1:nT, i] * psens[1:nT] + (1 - omega[1:nT, i]) * (1 - psens[1:nT])) +
          (1 - pprev) * prod(omega[1:nT, i] * (1-pspec[1:nT]) + (1 - omega[1:nT, i]) * (pspec[1:nT]))
      }
      
      for(k in 1:nT){
        psens[k] ~ dunif(0, 1)
        pspec[k] ~ dunif(0, 1)
      }
      
      pprev ~ dunif(0, 0.5)
      
      Te[1:n] ~ dmulti(pinf[1:n], N)
      
    })
    
    consts <- list(n = length(testcounts),
                   nT = ntests, N = sum(testcounts), omega = omega)
    
    data <- list(
      Te = testcounts)
    
    inits <- list(
      pprev = runif(1, 0, 0.5),
      psens = runif(ntests, 0.5, 1),
      pspec = runif(ntests, 0.5, 1)
    )
    
    model <- nimbleModel(code, constants = consts, data = data, inits = inits)
    
    cModel <- compileNimble(model)
    
    config <- configureMCMC(model)
    
    
    rMCMC <- buildMCMC(config)
    
    cMCMC <- compileNimble(rMCMC, project = model)
    
    system.time(run <- runMCMC(cMCMC, 
                                    niter = 50000, 
                                    nburnin = 2400, 
                                    nchains = 3, 
                                    progressBar = TRUE, 
                                    summary = TRUE, 
                                    samplesAsCodaMCMC = TRUE, 
                                    thin = 1))
    
    runsummary <- MCMCsummary(run$samples)
    runM <- as.matrix(run$samples)
    
    summaryinference[q, ] <- runsummary$mean
    summaryinfsd[q, ] <- runsummary$sd
    
  } # end loop over sensitivities
  
  summaryinference_all[iter, , ] <- summaryinference
  summaryinfsd_all[iter, , ] <- summaryinfsd

} # end loop over iterations

## Save data
saveRDS(summaryinference_all, "SummaryInference_ALL.rds")
saveRDS(summaryinfsd_all, "SummaryInferenceSD_ALL.rds")

```

#### We now load the results and process ready to plot.

```{r, message = FALSE}

summaryinference_all <- readRDS("SummaryInference_ALL.rds")
summaryinfsd_all <- readRDS("SummaryInferenceSD_ALL.rds")

# Create an empty data frame to hold the results
plot_data <- data.frame(iteration = integer(),
                        true_sens = double(),
                        inferred_sens = double(),
                        posterior_sd = double(),
                        posterior_mode = double())

# Loop through the 3D arrays to populate the data frame
for (iter in 1:dim(summaryinference_all)[1]) {
  for (q in 1:dim(summaryinference_all)[2]) {
    true_sens = psensvec[q]
    
    inferred_sens = summaryinference_all[iter, q, 2]
    posterior_sd = summaryinfsd_all[iter, q, 2]
   
    plot_data <- rbind(plot_data, data.frame(iteration = iter, true_sens = true_sens, 
                                             inferred_sens = inferred_sens, posterior_sd = posterior_sd))
  }
}
```

#### Now prepare each panel plot.

```{r, message = FALSE}

#A Plotting inferred vs true sensitivity
A <- ggplot(plot_data, aes(x = true_sens, y = inferred_sens)) +
  geom_point(alpha = 0.2, size = 5) +
  xlab("") +
  ylab("Inferred Sensitivity") +
  theme_bw() +
  theme(text = element_text(size = 13)) +
  geom_abline(slope = 1,
              intercept = 0,
              color="blue") +
  labs(title = "a")


#B Plotting within sample imprecision
B <- ggplot(plot_data, aes(x = true_sens, y = posterior_sd)) +
  geom_point(alpha = 0.2, size = 5) +
  xlab("") +
  ylab("Within sample imprecision") +
  theme_bw() +
  theme(text = element_text(size = 13)) +
  labs(title = "b")
 
#C Plotting among sample imprecision
C <- plot_data %>%
  group_by(true_sens) %>%
  mutate(sdMode = sd(inferred_sens)) %>%
  ungroup() %>%
  ggplot(aes(x = true_sens, y = sdMode)) +
  geom_point() +
  labs(x = "",
       y = "Among sample imprecision")  +
  theme_bw() +
  theme(text = element_text(size = 13)) +
  labs(title = "c")

# D
mean_diffs <- plot_data %>%
  mutate(diff = inferred_sens - true_sens) %>%
  group_by(true_sens) %>%
  summarise(mean_diff = mean(diff))

# D Plotting among sample inaccuracy
D <- ggplot(mean_diffs, aes(x = true_sens, y = mean_diff)) +
  geom_point() +
  labs(x = "",
       y = "Among sample inaccuracy")  +
  theme_bw() +
  theme(text = element_text(size = 13)) +
  ylim(-0.1, 0.1) +
  geom_abline(slope = 0, intercept = 0, colour = "black", linetype = "dashed") +
  labs (title = "d")

```

#### And finally generate the final plot.

```{r, message=FALSE}

Fig6 <- (A|B) /(C|D)

wrap_elements(panel = Fig6) +
  labs(tag = "True Sensitivity") +
  theme(
    plot.tag = element_text(size = 15),
    plot.tag.position = "bottom"
  )

```
